Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-27 colt-21/cvx-flats.tex
more 6

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

@@

In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2018elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.

@@

We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex-elicitation lower bounds.
The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.

@@

\begin{lemma}
	  \label{thm:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.  Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction, we know it is a $d$-flat.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
Let $p \in \relint{\P}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is consistent with respect to $\gamma$.
%
%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

@@

\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all calibrated convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{thm:convex-flats-inf-dim}.
So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.

%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
%\begin{lemma}\label{lem:Pcodim-codim-finite}
%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
%\end{lemma}
%\begin{proof}
%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
%	
%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
%\end{proof}

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

@@

\begin{figure}[ht]
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
		$\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}(${\color{blue}\textbullet}$)) = 1$\vspace*{-5pt}}
	\label{fig:fsd-bound}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
	However, there is a $1$-flat containing {\color{blue} \textbullet} that is a subset of $\gamma_\bot$ and $\gamma_3$.
	}
	\label{fig:flats-bound}
\end{minipage}
\end{figure}

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
In this setting, Lemma~\ref{thm:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular,
% following an argument from~\citet{frongillo2018elicitation},
Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.

These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2018elicitation}?  Do we need to change that citation.}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
The lower bounds of that work are essentially all with respect to identifiable properties, that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$.
In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats (see Figure~\ref{fig:fsd-bound}).
Establishing a theory of elicitation complexity for convex-elicitable properties therefore seemed to require entirely new ideas.
Surprisingly, we show that the central techniques of~\citet{frongillo2020elicitation} also apply to convex-elicitable properties, via Lemma~\ref{thm:convex-flats-inf-dim}.
In particular, we can recover their main lower bound for the large class of Bayes risks.

% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
% While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.

% When extending the results of~\cite{frongillo2018elicitation}, we assume a property is identifiable, meaning its level sets are flats.
% \begin{definition}
%   A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
%   We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
% \end{definition}

\begin{condition}\label{cond:v-interior}
  There exists $r\in\range\Gamma$, such that $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.  I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
\end{condition}

@@

\citet{frongillo2018elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
In particular, for $0 < \alpha < 1$, we may define
\begin{align}
  \CVaR_\alpha(p)
  &= \inf_{r\in\reals} \E_p\left\{ \tfrac 1 \alpha(r-Y)\ones_{r\geq Y}- r\right\}~,
  \label{eq:elic-complex-es-3}
\end{align}
which is the Bayes risk of the transformed pinball loss $L_\alpha(r,y) = \tfrac 1 \alpha(r-y)\ones_{r\geq y}-r$.
In turn, $L_\alpha$ elicits the $\alpha$-quantile $q_\alpha(p) = \raf{DEF}$.

>>>>

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{steinwart2008support,agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2020elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
For discrete target losses, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.\jessiet{Discussion about how this is really about consistency}
Their results have led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.

@@

In the case of a target statistic/property $\gamma$, \citet{lambert2008eliciting} similarly introduce the notion of \emph{elicitation complexity}, later generalized by \citet{frongillo2020elicitation}, which captures the lowest prediction dimension of a surrogate which indirectly elicits $\gamma$.
This notion is more general as it extends to continuous estimation settings and does not inherently depend on a target loss being given. 
% However, until now, no formal connection to consistency has been shown for convex elicitation complexity.

@@

We now turn to the question of bounding the prediction dimension of a consistent convex surrogate.
From Theorem \ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the prediction dimension of a convex surrogate indirectly eliciting $\gamma$.
We now explore two tools, Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop}, for proving such convex-elicitation lower bounds.
The key idea, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem~9]{agarwal2015consistent}, is to consider a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ with is optimal for $p$.
Theorem~\ref{lem:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat}.
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
The use of this result is to leverage the contrapositive: if $\gamma$ has a level set intricate enough to not contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent surrogate.

@@

\begin{lemma}
	  \label{lem:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by a convex $L \in \L_d$ for some $d\in\mathbb{N}$.
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
	\jessie{Direct}
		As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
		We proceed in two cases, depending on $|\Y|$.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$\raft{To discuss next meeting: maybe it's better to say $\eliccvx(\gamma) > d$ instead of the indirectly elicits bit.  Both here and the next Cor.}, and in particular, there is no convex surrogate $L \in \L_d$ that is  consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction, we know it is a $d$-flat.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
Let $p \in \relint{\P}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ that is consistent with respect to $\gamma$.
%
%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{lem:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

@@

\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all calibrated convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{lem:convex-flats-inf-dim}.
So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.

%\jessie{I think this Lemma can be moved to the Appendix; just leaving it here for now to make sure it gets eyes on it.}
%\begin{lemma}\label{lem:Pcodim-codim-finite}
%	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
%	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
%\end{lemma}
%\begin{proof}
%	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{lem:convex-flats-inf-dim} (recall $F = \zeros{V}$).
%	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.
%	
%	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
%	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
%\end{proof}

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
	Lemma~\ref{lem:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \Scr_F(p) \geq n - d- 1$ is given by Lemma~\ref{lem:finite-relint-dim} (ii).
%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

@@

\begin{figure}[ht]
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\scalebox{0.5}{$\bigstar$}})) = 1$.
          \raf{Jessie: for color reasons, maybe we could make the blue one a different symbol?  Here's my attempt... could be touched up :-)}
          \vspace*{-5pt}
        }
	\label{fig:fsd-bound}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
	However, there is a $1$-flat containing {\color{blue} \textbullet} that is a subset of $\gamma_\bot$ and $\gamma_3$.
	}
	\label{fig:flats-bound}
\end{minipage}
\end{figure}

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one is not given a target loss, but instead a target (conditional) statistic of the data one wishes to estimate, such as the mean or variance.
In this setting, Lemma~\ref{lem:convex-flats-inf-dim} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular,
% following an argument from~\citet{frongillo2020elicitation},
Theorem~\ref{thm:bayes-risk-lower-bound} below yields new bounds on the convex elicitation complexity of statistics which quantify risk or uncertainty such as variance, entropy, or financial risk measures.

These bounds address an open question of~\citet{frongillo2020elicitation}\jessiet{Is this the same as~\cite{frongillo2020elicitation}?  Do we need to change that citation.}\raft{Yeah, all should be the 2020 now, and eventually 2021.  Burn after reading :-)}, that of developing a theory of elicitation complexity for with respect to convex-elicitable properties.
The lower bounds of previous work are essentially all with respect to \emph{identifiable} properties, whose levels sets are all flats.
%that is, properties $\gamma$ for which there is some $d$ where $\gamma_r$ is a $d$-flat for all $r\in\R$
In contrast, properties elicited by non-smooth convex losses are generally not identifiable.
For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats: from Figure~\ref{fig:fsd-bound}, we can see that any affine space containing a level set of the abstain property would contain the entire simplex.
Establishing a theory of elicitation complexity for convex-elicitable properties therefore seems to require entirely new ideas.

Surprisingly, we show that one can adapt the techniques of~\citet{frongillo2020elicitation} to convex-elicitable properties.
In essence, their techniques rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain a single $d$-flat.
One concludes that one cannot indirectly elicit $\gamma$ via a $d$-dimensional identifiable property $\hat\Gamma$, as the level sets of $\hat\Gamma$, each $d$-flats, could not be contained within level sets of $\gamma$.
Lemma~\ref{lem:convex-flats-inf-dim} states that the level sets of $d$-dimensional convex-elicitable properties are unions of $d$-flats, and thus the general logic of~\citet{frongillo2020elicitation} can still apply.
In particular, we can recover their main lower bound for the large class of Bayes risks.

% Theorem~\ref{thm:cvx-flats} also addresses one major open question  from~\citet{frongillo2015elicitation,frongillo2020elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
% While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
% Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2020elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.

% When extending the results of~\cite{frongillo2020elicitation}, we assume a property is identifiable, meaning its level sets are flats.
% \begin{definition}
%   A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
%   We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
% \end{definition}

\begin{condition}\label{cond:v-interior}
  For some $r\in\range\Gamma$, the level set $\Gamma_r = \zeros{V}$ is a $d$-flat presented by some $V:\Y\to\reals^d$ such that \raft{I think we only need $\Gamma_r \subseteq \zeros{V}$.  I think I'll update the proof at some point to reflect this, since it actually gets a bit easier to follow.} $0\in\interior\{\E_pV : p\in\P\}$.
\end{condition}

@@

\citet{frongillo2020elicitation} observe that one of the most prominent financial risk measures, the conditional value at risk (CVaR), can be expressed as a Bayes risk.
In particular, for $0 < \alpha < 1$, we may define
\begin{align}
  \CVaR_\alpha(p)
  &= \inf_{r\in\reals} \E_p\left\{ \tfrac 1 \alpha(r-Y)\ones_{r\geq Y}- r\right\}~,
  \label{eq:elic-complex-es-3}
\end{align}
which is the Bayes risk of the transformed pinball loss $L_\alpha(r,y) = \tfrac 1 \alpha(r-y)\ones_{r\geq y}-r$.
In turn, $L_\alpha$ elicits the $\alpha$-quantile $q_\alpha(p) = \raf{DEF}$.
